---
title: "Predict the delay of each flight using ridgereg()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Predict the delay of each flight using ridgereg()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Step 1: Scale down the dataset
Scale down the **flights** dataset to half.
```{r}
library(nycflights13)
library(dplyr)

set.seed(42)
sampled_flights_data <- slice_sample(flights, prop = 0.5)
```

## Step 2: Remove irrelative variables
In **flights** dataset, *dep_delay* is the dependent variable. *origin* and *time_hour* are for combining with **weather** dataset. The rest variables are useless.  
In **weather** dataset, *origin* and *time_hour* are for combining with **flights** dataset. All variables related to weather are regarded as having a predictive value. *year*, *month*, *day*, and *hour* are useless because *time_hour* is enough.
```{r}
flights_data <- select(sampled_flights_data, -c(year,month,day,dep_time,sched_dep_time,arr_time,sched_arr_time,arr_delay,carrier,flight,tailnum,dest,air_time,distance,hour,minute)) 

weather_data <- select(weather, -c(year,month,day,hour))
```

