---
title: "Predict the delay of each flight using ridgereg()"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Predict the delay of each flight using ridgereg()}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Step 1: Scale down the dataset
Scale down the **flights** dataset to its half.
```{r}
library(nycflights13)
library(dplyr)

set.seed(42)
sampled_flights_data <- slice_sample(flights, prop = 0.5)
```

## Step 2: Remove irrelative variables
In **flights** dataset, *dep_delay* is the dependent variable. *origin* and *time_hour* are for combining with **weather** dataset. The rest variables are irrelative.  
In **weather** dataset, *origin* and *time_hour* are for combining with **flights** dataset. *year*, *month*, *day*, and *hour* are useless because *time_hour* is enough. Also, we reckon *wind_dir*, *wind_speed*, and *pressure* are irrelative.
```{r}
flights_data <- select(sampled_flights_data, -c(year,month,day,dep_time,sched_dep_time,arr_time,sched_arr_time,arr_delay,carrier,flight,tailnum,dest,air_time,distance,hour,minute)) 
weather_data <- select(weather, -c(year,month,day,hour,wind_dir,wind_speed,pressure))
```

## Step 3: Add extra weather data
Heavy rainfall and bad visibility weather conditions may have an impact on flight takeoffs. Thus, a variable named *precip_visib* created which equals $precip/visib$.
```{r}
weather_data <- mutate(weather_data,precip_visib = precip/visib)
```

## Step 4: Divide the flight dataset into training, test and validation sets
Firstly, combine the **weather** dataset to **flights** dataset based on *origin* and *time_hour*.
```{r}
merged_data <- flights_data %>% left_join(weather_data, by = c("origin", "time_hour"))
```

Secondly, delete *origin* and *time_hour*.
```{r}
flight_weather_data <- select(merged_data,-c("origin", "time_hour"))
flight_weather_data <- na.omit(flight_weather_data)
flight_weather_data <- as.data.frame(flight_weather_data)
```

Then, divide the dataset into three sets.
```{r}
library(caret)
set.seed(42)
training_idx <- createDataPartition(flight_weather_data$dep_delay, 
                                    p = 0.8, 
                                    list = FALSE)
trainingset <- flight_weather_data[training_idx,]
test_valid_data <- flight_weather_data[-training_idx,]
set.seed(42)
test_idx <- createDataPartition(test_valid_data$dep_delay, 
                                    p = 0.25, 
                                    list = FALSE)
testset <- test_valid_data[test_idx,]
validset <- test_valid_data[-test_idx,]
```

## Step 5: Find the best $\lambda$
```{r}
library(lab4package)

lambda_RMSE_list <- list(lambda = numeric(0),RMSE = numeric(0))
lambda_range <- c(0,10^seq(-3, 4, by = 0.1))
valid_actual_value <- validset$dep_delay
i <- 1

for (m in lambda_range){
  flight_delays_model <- ridgereg$new(dep_delay~.,trainingset,m)
  valid_predict_value <- flight_delays_model$predict(validset[,-1])
  valid_RMSE <- sqrt(mean((valid_actual_value-valid_predict_value)^2))
  
  lambda_RMSE_list$lambda[i] <- m
  lambda_RMSE_list$RMSE[i] <- valid_RMSE
  i = i+1
}

lambda_RMSE_df <- data.frame(lambda_RMSE_list)
optimal_lambda <- lambda_RMSE_df$lambda[which.min(lambda_RMSE_df$RMSE)]
plot(lambda_RMSE_df$lambda, lambda_RMSE_df$RMSE, log = "x", type = "o")
print(optimal_lambda)
```
## Step 6: Predict the test set
```{r}
test_actual_value <- testset$dep_delay

flight_delays_model <- ridgereg$new(dep_delay~.,trainingset,optimal_lambda)
test_predict_value <- flight_delays_model$predict(testset[,-1])
test_RMSE <- sqrt(mean((test_actual_value-test_predict_value)^2))
print(test_RMSE)
```
