---
title: "Guide for lab4package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Guide for lab4package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Description
This package offers a RC class function that can analyze linear regression models like what *lm()* can do.

## Import
```{r setup}
library(lab4package)
```

## Instantiation
The first argument is a formula and the second argument is a data frame. Here takes *iris* for demonstration.
```{r}
data(iris)
linreg_mod <- linreg$new(Petal.Length~Species, data=iris)
```

## Methods
Below are the methods that this package offers.

### print()
This will print out the function call and the coefficients of the independent variables.
```{r}
linreg_mod$print()
```
### plot()
This will print out two plots helping analyze the outcomes.
```{r}
linreg_mod$plot()
```

### resid()
This will generate the residuals of the observations, which are the differences between the actual values and the predicted values.
```{r}
linreg_mod$resid()
```
### pred()
This can print out the predicted values.
```{r}
linreg_mod$pred()
```
### coef()
This will print out the coefficients of the independent variables. 
```{r}
linreg_mod$coef()
```
### summary()
This will give a summary of the linear regression model.
```{r}
linreg_mod$summary()
```




